---
title: "p8105_hw1_zf2212"
author: "Catherine"
date: "9/13/2018"
output: github_document
---
# Problem 1

```{r problem_1, warning = FALSE}
library(tidyverse)

## set seed to ensure reproducibility

set.seed(123)

## create a data frame

hw1_df = tibble(
  samp = runif(10, min = 0, max = 5),
  vec_logical = samp > 2,
  vec_char = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
  vec_factor = factor(c("1", "0", "1", "1", "1", "0", "1", "1", "1", "0"))
)  

mean(hw1_df$samp)
mean(hw1_df$vec_logical)
mean(hw1_df$vec_char)
mean(hw1_df$vec_factor)

```
Numeric and logical vector works, character and factor vector doesn't.

```{r convert_to_numeric, eval = FALSE}

vec_logical_num = as.numeric(hw1_df$vec_logical)
vec_char_num = as.numeric(hw1_df$vec_char)
vec_factor_num = as.numeric(hw1_df$vec_factor)

```
Convert the logical, character, and factor variables to numeric.

```{r more_convert}

vec_char_factor = as.factor(hw1_df$vec_char)
vec_char_factor_num = as.numeric(vec_char_factor)
vec_factor_char = as.character(hw1_df$vec_factor)
vec_factor_char_num = as.numeric(vec_factor_char)

```
Convert charater variables to factor to numeric.
Convert factor variables to character to numeric.

# Problem 2

```{r}
set.seed(123)

plot_df = tibble(
  x = rnorm(1000, mean = 0, sd = 1),
  y = rnorm(1000, mean = 0, sd = 1),
  logical_xy = x + y > 0,
  logical_xy_num = as.numeric(logical_xy),
  logical_xy_factor = as.factor(logical_xy)
)
```

The **size of the dataset** is `r dim(plot_df)`. 
The **mean** of x is `r mean(plot_df$x)` and the **median** of x is `r median(plot_df$x)`.
The **proportion** of cases for _which the logical vector is TRUE_ is `r mean(plot_df$logical_xy)`.

```{r}
ggplot(plot_df, aes(x = x, y = y, color = logical_xy)) + geom_point()
ggsave("plot_logical.pdf", height = 4, width = 6)
```
The scatterplot of y vs x differentiate color points using the logical variable. Blue represents the TRUE and red represents the FALSE.

```{r}
ggplot(plot_df, aes(x = x, y = y, color = logical_xy_num)) + geom_point()
ggsave("plot_numeric.pdf", height = 4, width = 6)
```
The scatterplot of y vs x differentiate color points using the numeric variable. The black represents 0 which is FALSE. The blue represents 1 which is TRUE.

```{r}
ggplot(plot_df, aes(x = x, y = y, color = logical_xy_factor)) + geom_point()
ggsave("plot_factor.pdf", height = 4, width = 6)
```
The scatterplot of y vs x differentiate color points using the factor variable. Blue represents the TRUE and red represents the FALSE.
